|

### 2023-05-12 paper/04-results.Rmd
more work

```{r}
#| label: fig_crosby_curves
#| fig.cap: "Changes in STRAIN, velocity, and distance from the QB for Maxx Crosby over the course of a successful pass rush play that results in a sack."
#| fig.width: 4.8
#| fig.height: 2.7
source(here("scripts", "02_fig_crosby_curves.R"))
fig_crosby_curves
```

@@

```{r}
#| label: fig_crosby_curves_unsucess
#| fig.cap: "Changes in STRAIN, velocity, and distance from the QB for Maxx Crosby over the course of an unsuccessful pass rush play."
#| fig.width: 4.8
#| fig.height: 2.7
source(here("scripts", "09_fig_play_unsuccess.R"))
fig_crosby_curves_unsucess
```

@@

[CHECK THIS, MAKE SURE WORDING IS CORRECT/NOT CONFUSING]

@@

We observe statistically significant differences among the pass rush and pass block positions in most cases, while controlling for other variables.
The coefficient estimates for the pass rush position terms reveal that players with positions closer to the line of scrimmage (DT and NT) appear to generate less STRAIN (relative to DE) than those that are further back, which is consistent with our results in Section \ref{sec:positional}.
For blockers, centers are those that absorb the most pressure on average, compared to the baseline level tackles, guards, and other offensive positions.

@@

In addition to adjusting for opposition, our multilevel model allows us to provide some notion of uncertainty about the pass rusher's effect on the play level STRAIN.
Figure \ref{fig:fig_rankings_boot} displays the mean varying intercept for the top ten pass rushers for each position along with 95% confidence intervals generated by sampling from the posterior distributions via parametric bootstrapping using the `merTools` package [@knowlesmerTools, @gelman2006data]. 
We observe similar rankings based on the random intercepts in comparison to the average STRAIN results in Tables \ref{tab:edge} and \ref{tab:interior}, with Myles Garrett (DE), Aaron Donald (DT), Vita Vea (NT), and T.J. Watt (OLB) as the top pass rusher for their respective position. 
We observe different levels of variability across these top players, with the only a subset of players with intervals strictly above zero.
[NEED TO THINK ABOUT WHAT MORE TO SAY HERE]

>>>>

```{r}
#| label: fig_crosby_curves
#| fig.cap: "Changes in STRAIN, velocity, and distance from the QB for Maxx Crosby over the course of a successful pass rush play that results in a sack. The STRAIN for other pass rushers throughout this play is also displayed."
#| fig.width: 4.8
#| fig.height: 2.7
source(here("scripts", "02_fig_crosby_curves.R"))
fig_crosby_curves
```

@@

```{r}
#| label: fig_crosby_curves_unsucess
#| fig.cap: "Changes in STRAIN, velocity, and distance from the QB for Maxx Crosby over the course of an unsuccessful pass rush play. The STRAIN for other pass rushers throughout this play is also displayed."
#| fig.width: 4.8
#| fig.height: 2.7
source(here("scripts", "09_fig_play_unsuccess.R"))
fig_crosby_curves_unsucess
```

@@

[CHECK/EDIT THIS, MAKE SURE WORDING IS CORRECT/NOT CONFUSING]

@@

We observe statistically significant differences among the pass rush and pass block positions in most cases, while controlling for other variables.
The coefficient estimates for the pass rush position terms reveal that players with positions closer to the line of scrimmage (DT and NT) appear to generate less STRAIN (relative to DE) than those that are further back, which is consistent with our results in Section \ref{sec:positional}.
For blockers, centers are those that absorb the most pressure on average, more than guards and other offensive positions (compared to the baseline level, tackles).

@@

In addition to adjusting for opposition, our multilevel model allows us to provide some notion of uncertainty about the pass rusher's effect on the play level STRAIN.
Figure \ref{fig:fig_rankings_boot} displays the mean varying intercept for the top ten pass rushers for each position along with 95% confidence intervals generated by sampling from the posterior distributions via parametric bootstrapping using the `merTools` package [@knowlesmerTools, @gelman2006data]. 
We observe similar rankings based on the random intercepts in comparison to the average STRAIN results in Tables \ref{tab:edge} and \ref{tab:interior}, with Myles Garrett (DE), Aaron Donald (DT), Vita Vea (NT), and T.J. Watt (OLB) as the top pass rusher for their respective position. 
We observe different levels of variability across these top players, with the only a subset of players with intervals strictly above zero.

[NEED TO THINK ABOUT WHAT MORE TO SAY HERE]
